Rotation effects on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-05-31 paper/Analisis.tex
minor changes

The results for these outgoing spectra are integrated over the whole
sphere, meaning that all the escaping photons were taking into account
regardless of the direction of the outgoing photons. Figure
\ref{fig:differentobservers} shows how if one gives a weight to each outgoing
photon according to its direction when escaping the gas distribution
it is possible to detect notable differences in the spectrum for
different viewing angles.

@@

Figure~\ref{fig:widthvsvelocity} summarizes our findings for $W_{1/2}$
as a function of $V_{\rm max}$. The line width increases with the
rotational velocity of the gas cloud. This increase can be of a factor
of $2-3$ with respect to the width with respect to the static
case. This trend is conserved at all optical depths regardless of the
initial source distribution.

%Im not sure about this anymore
This result includes all the outgoing photons, regardless of the
position of the observer. In Figure~\ref{fig:widthvstheta} we
take into account the different positions of the observer in the
measurement of the half-width $W_{1/2}$. From this we conclude
that observers with a line of sight perpendicular to the axis of
rotation (i.e. edge-on in the case of spiral galaxy) tend to measure
larger line widths than observers aligned with the rotation axis
(i.e. face-on). The influence of the observer position on the line
width, amounting always less than $15\%$ of a difference with respect
to the result that takes into account all the outgoing photons with
the same weight regardless of the relative observer position.

@@

In Figure~\ref{fig:maximumsvsvelocity} we present the position
of the maxima as a function of $V_{\rm max}$. For the photons emitted
in the line center we do not find any variation in the position of the
maxima in the range of explored parameter space (dash lines). However in the
homogeneous case we can see how the maxima goes to $x_{m}=0$, meaning
that the double peak is converted into a single peak.

@@

Finally we also report on the effect of the neutral Hydrogen
optical depth $\tau_{H}$ on the maxima position $x_{m}$
Figure~\ref{fig:maximumsvsvelocity}. We find that, at fixed
rotation velocity, the position of the maxima increases with optical
depth as expected from basic theoretical considerations. We compare
our results with the expected theoretical scaling for an infinite
slab.

@@

Until know we have focus in how rotation affect the morphology of the Lyman alpha line, now we turn to study deeply the possible causes of this effects. As recombination is the main cause of the emission of the Lyman alpha line, it is important to study the relationship between the number of times that a photon is absorbed and re emitted hereafter scatterings with it's shift in the wavelength.

@@

In order to understand the effects of rotation in the morphology of the line we make histograms of $<N_{scatt}>$  in function of $X_{m}$ for both the central Fig.~\ref{fig:NscattHisto} and the  homogeneous distribution Fig.~\ref{fig:NscattHistoHOM}. For the central distribution and for lower velocities we found that for some value (put the value) of $N_{scatt}$ the mayority of photons have a defined value of $X_{m}$. While for higher velocities photons tend spread out in $X_{m}$(Make position analysis of this photons).\\

@@

\begin{figure}
    \includegraphics[width=0.54\textwidth]{test4.png}%this is the central}
\caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution\label{fig:NscattHisto}} 
\end{figure}

@@

    \caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the homogeneous distribution\label{fig:NscattHistoHOM}} 
\end{figure}

>>>>

The results for these outgoing spectra are integrated over the whole
sphere, meaning that all the escaping photons were taking into account
regardless of the direction of the outgoing photons. Fig.~\ref{fig:differentobservers}
shows how if one gives a weight to each outgoing
photon according to its direction when escaping the gas distribution
it is possible to detect notable differences in the spectrum for
different viewing angles.

@@

Fig.~\ref{fig:widthvsvelocity} summarizes our findings for $W_{1/2}$
as a function of $V_{\rm max}$. The line width increases with the
rotational velocity of the gas cloud. This increase can be of a factor
of $2-3$ with respect to the width with respect to the static
case. This trend is conserved at all optical depths regardless of the
initial source distribution.

%Im not sure about this anymore---TALK to Jaime about this!
This result includes all the outgoing photons, regardless of the
position of the observer. In Figure~\ref{fig:widthvstheta} we
take into account the different positions of the observer in the
measurement of the half-width $W_{1/2}$. From this we conclude
that observers with a line of sight perpendicular to the axis of
rotation (i.e. edge-on in the case of spiral galaxy) tend to measure
larger line widths than observers aligned with the rotation axis
(i.e. face-on). The influence of the observer position on the line
width, amounting always less than $15\%$ of a difference with respect
to the result that takes into account all the outgoing photons with
the same weight regardless of the relative observer position.

@@

In Fig.~\ref{fig:maximumsvsvelocity} we present the position
of the maxima as a function of $V_{\rm max}$. For the photons emitted
in the line center we do not find any variation in the position of the
maxima in the range of explored parameter space (dash lines). However in the
homogeneous case we can see how the maxima goes to $x_{m}=0$, meaning
that the double peak is converted into a single peak.

@@

Finally we also report on the effect of the neutral Hydrogen
optical depth $\tau_{H}$ on the maxima position $x_{m}$
Fig.~\ref{fig:maximumsvsvelocity}. We find that, at fixed
rotation velocity, the position of the maxima increases with optical
depth as expected from basic theoretical considerations. We compare
our results with the expected theoretical scaling for an infinite
slab.

@@

Until know we have focus in how rotation affect the morphology of the 
Lyman alpha line, now we turn to study deeply the possible causes of 
this effects. As recombination is the main cause of the emission of the 
Lyman alpha line, it is important to study the relationship between the 
number of times that a photon is absorbed and re emitted that we simply 
take as scatterings with it's shift in the wavelength.

@@

In order to understand the effects of rotation in the morphology of the line
 we make histograms of $<N_{scatt}>$  in function of $X_{m}$ for both the 
 central Fig.~\ref{fig:NscattHisto} and the  homogeneous distribution 
 Fig.~\ref{fig:NscattHistoHOM}. For the central distribution and for lower 
 velocities we found that for some value (put the value) of $N_{scatt}$ the 
 mayority of photons have a defined value of $X_{m}$. While for higher 
 velocities photons tend spread out in $X_{m}$(Make position analysis of 
 this photons).

@@

\begin{figure}
    \includegraphics[width=0.54\textwidth]{test4.png}%this is the central}
\caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution, The upper plot is for $V_{max}=50km/s $, the bottom plot is for $V_{max}=300km/s$ \label{fig:NscattHisto}} 
\end{figure}

@@

    \caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the homogeneous distribution, The upper plot is for $V_{max}=50km/s $, the bottom plot is for $V_{max}=300km/s$ \label{fig:NscattHistoHOM}} 
\end{figure}
